\hspace{1cm} Do syntactic and semantic similarity lead to interference effects? \newline Evidence from self-paced reading and event-related potentials using German

### 2024-08-20 paper/main.tex
minor edit

\textcolor{blue}{The Bayes factors under different priors on $F$ are shown in Figure \ref{fig:BF_compmods}. Compared to the null model, the one-cue model, the Bayes factors indicate strong evidence for the new two-cues model. Therefore, we can conclude that the computational modeling shows that our data shows interference. Compared to the three-cues model proposed by \textcite{mertzen}, the Bayes factors provide moderate evidence for the new two-cues model. Therefore, the assumption that the relevant syntactic cue is the \{$\pm$subject-in-same-clause\} cue – rather than the previously assumed \{$\pm$grammatical subject\} cue – is moderately supported by these modeling results. This result holds for prior assumptions that allows higher probability mass for small values of $F$., i.e., for $F<0.01$.}

>>>>

\textcolor{blue}{The Bayes factors under different priors on $F$ are shown in Figure \ref{fig:BF_compmods}. Compared to the null model, the one-cue model, the Bayes factors indicate strong evidence for the new two-cues model; this comparison shows that there is strong evidence for interference effects. Compared to the three-cues model proposed by \textcite{mertzen}, the Bayes factors provide moderate evidence for the new two-cues model. This model comparison shows that there is some support for the idea that the relevant syntactic cue is the \{$\pm$subject-in-same-clause\} cue – rather than the previously assumed \{$\pm$grammatical subject\} cue. This result holds for prior assumptions that allows higher probability mass for small values of $F$., i.e., for $F<0.01$.}
